---
title: "Untitled"
output: html_document
date: "2022-09-15"
---
3.7--9
```{r}
library(MASS)
library(ISLR)
Auto = na.omit(Auto)
names(Auto)
```

#a
```{r}
pairs(Auto[1:8])
```

#b
```{r}
cor(Auto[1:8])
```
```{r}
round(cor(Auto[1:8]), digits = 3)       #将函数四舍五入
```


#c
```{r}
mpg = lm(mpg~.-name,data=Auto)
summary(mpg)
```
1, F = 252.4, p=0.00, strong relationship between predictor and response;
2, displacement, weight, year, origin;
3, coefficient = 0.75, suggests year + 1, mpg + 0.75;



#d
```{r}
par(mfrow=c(2,2))
plot(mpg)
par(mfrow = c(1,1))
plot(hatvalues(mpg))
which.max(hatvalues(mpg))
library(car)
vif(mpg)
```
The residual plot suggests there may be non-linear relationship; 
According to residuals vs leverage plot and hatvalues plot, 14 may be high leverage observation.


#e
```{r}
#professor
mpg0 = lm(mpg~.-name + year:horsepower + horsepower:displacement,data=Auto)
summary(mpg0)

#mine
mpg1 = lm(mpg~.-name + year:origin + weight:displacement,data=Auto)
summary(mpg1)
```

All the interaction predictors in each model are significant, so there may be interaction effects.


#f
```{r}
#professor
mpg2 = lm(mpg~.-name + I(weight^2) + I(displacement^2), data = Auto)
summary(mpg2)

#mine
mpg3 = lm(mpg~.-name + log(year) + log(weight), data = Auto)
summary(mpg3)
```

Model with log predictor seems perform better. 