---
title: "Lab3"
author: "DuraiSundaramoorthi"
output: pdf_document
---

## 3.6.2 Simple Linear Regression
## Boston Data-Set in package MASS
##Code Chunk 1
```{r}
library(MASS)

fix(Boston)

names(Boston)
```

##Fitting linear regression
##Code Chunk 2
```{r}
lm.fit=lm(medv~lstat) ##calling lm function without mentioning data set

lm.fit=lm(medv~lstat, data = Boston)## Proper way to call lm()

attach(Boston) ##attaching lets use lm without referencing to the data set

lm.fit=lm(medv~lstat) 

```

## Model Summary
##Code Chunk 3
```{r}
lm.fit ##basic information about the model output

summary(lm.fit) ##more information about the model output

names(lm.fit) ##other information in lm.fit

lm.fit$coefficients ##explicitly asking for co-efficients in lm.fit

coef(lm.fit) ## another way

confint(lm.fit) ## confidence interval for Betas
```

##confidence interval and prediction interval for medv at a value of lstat
##Code Chunk 4
```{r}
predict(lm.fit,data.frame(lstat=c(5,10,15)),interval="confidence")

predict(lm.fit,data.frame(lstat=c(5,10,15)),interval="prediction")
```

##plot the fitted model
##lwd - controls width of the line; pch - controls plotting symbols
##Code Chunk 5
```{r}
plot(lstat,medv)
abline(lm.fit)

plot(lstat,medv)
abline(lm.fit,lwd=3) ##line becomes 3 times wider

plot(lstat,medv)
abline(lm.fit,lwd=3,col = "red")

plot(lstat,medv,col="red")

plot(lstat,medv,pch=7)
 
plot(lstat,medv,pch="+")

plot(1:20,1:20,pch=1:20)
```


## More Plots
##Code Chunk 6
```{r}
par(mfrow=c(2,2)) ##divide plotting region into 2*2

plot(lm.fit)

par(mfrow=c(1,1)) ##reset plotting region

plot(predict(lm.fit),residuals(lm.fit))

plot(predict(lm.fit),rstudent(lm.fit))

plot(hatvalues(lm.fit)) ##Leverage

which.max(hatvalues(lm.fit))##the observation with the largest leverage statistic
```


## 3.6.3 Multiple Linear Regression
##Code Chunk 7
```{r}
lm.fit=lm(medv~lstat+age,data=Boston)

summary(lm.fit)

lm.fit=lm(medv~.,data=Boston) ##all predictors

summary(lm.fit)
```

## Getting model stats
##Code Chunk 8
```{r}
names(lm.fit)

summary(lm.fit)$r.sq ##Getting R^2

summary(lm.fit)$sigma ## Getting RSE

library(car) ##for calculating VIF

vif(lm.fit)##library car needed to get vif
```

##Excluding Variables
##Code Chunk 9
```{r}
lm.fit1=lm(medv~.-age,data =Boston) ##excluding one variable from the model

summary(lm(medv~.-age,data =Boston))

lm.fit1=update(lm.fit,~.-age)##update can be used to update the model

summary(update(lm.fit,~.-age))

```

## 3.6.4 Interaction
##Code Chunk 10
```{r}
summary(lm(medv~lstat*age,data=Boston))

summary(lm(medv~lstat:age,data=Boston))

```


## 3.6.5 Non-Linear Transformations
##Code Chunk 11
```{r}
lm.fit2=lm(medv~lstat+I(lstat^2),data=Boston)

summary(lm.fit2)

lm.fit=lm(medv~lstat, data=Boston)

##Ho = both models fit identically
##Ha = the full model is superior

anova(lm.fit,lm.fit2)
```


##poly() function for higher order
##Code Chunk 12
```{r}
lm.fit5=lm(medv~poly(lstat,5)) ##UPTO fifth degree

summary(lm.fit5)

summary(lm(medv~log(rm),data=Boston))##log transformation

```


## Carseats Data
##Code Chunk 13
```{r}
library(ISLR)

attach(Carseats)

?Carseats

fix(Carseats)

names(Carseats)
```

## Qualitative Predictors
##R generates dummy variables automatically
##Code Chunk 14
```{r}
lm.fit=lm(Sales~.+Income:Advertising+Price:Age,data = Carseats)

summary(lm.fit)

contrasts(ShelveLoc) ##contrasts() function returns the coding that R uses for the dummy variables

contrasts(US)
```

## 3.6.7 Writing Functions
##Code Chunk 15
```{r}
##Creating a function to load two libraries
LoadLibraries = function(){
   library(ISLR)
   library(MASS)
   print("The libraries ISLR and MASS have been loaded")
}
## following code tells what is inside the function
LoadLibraries

## following code runs the function
LoadLibraries()

```

## MyMean()
##Code Chunk 16
```{r}
MyMean = function(a,b){
  (a+b)/2
}
MyMean(2,3)
MyMean(5,55)
```